Blame and Coercion: Together Again for the Second Time

### 2019-10-18 paper.tex
comment
revert value and cast everywhere

\newcommand{\eOOcast}[4]{\langle \cOOcast{#2}{#3}{#4} \rangle #1}

@@

@@

%\newcommand{\cOOcast}[3]{#3 \overset{#2}{\Leftarrow} #1}
\newcommand{\cOOcast}[3]{#3 \Leftarrow^{#2} #1}
\newcommand{\vOOcast}[2]{\langle#2\rangle#1}

@@

	\redrule{
		\sOOreturn{v}{(
			\mathtt{cast} \; c \; \kappa
			)}
	}{
\begin{cases}
	\sOOreturn{u}{\kappa} & \sidecond{applyCast(c,v) = \rOOsucc{u}}
	\\
	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(c,v) = \rOOfail{l}}
\end{cases}
	}{}
\redrule{
\sOOreturn{v}{\kOOmt}}{
\sOOhalt{observe(v)}}{}

@@

\todo[inline]{Change the order of parameters for applyCast to take
	the value first and the cast second. -JS
	\\---\\
	Could you tell me why taking the value first is better?
	I am always taking the target of induction first. -KC
	\\---\\
    It's better because it matches the postfix syntax we are using for
    casts. Currently line 2 of applyCast for D is difficult to read,
    compare it with line 4 of applyCast for UD. -JS
    \\---\\
    Does it mean changing the syntax for casts to a prefix syntax would work as 
    well? 
    If yes, I prefer this way, because of the reason in my first response 
    and that function applications (apply) also takes arguments in this order.
    I have fixed it with my idea so that we can see if it works. This change is 
    easy to undo.
    -KC
    \\---\\
    Postfix is better than prefix because then the casts read left to right,
    which is the normal direction for English readers.
    Please make it so. -JS
    }

@@

	\fbox{$applyCast(c,v) = r$}
	\[
	\begin{array}{rclr}
	\funrule{
		applyCast(\cOOcast{\star}{l}{\star},v)
	}{
		\rOOsucc{v}
	}{}
	\funrule{
		applyCast(\cOOcast{\star}{l}{P_2},\vOOcast{v}{\cOOcast{P_1}{l'}{\star}})
	}{
		applyCast(\cOOcast{P_1}{l}{P_2},v)
	}{}
	\funrule{
		applyCast(\cOOcast{P}{l}{\star},v)
	}{
		\rOOsucc{\vOOcast{v}{\cOOcast{P}{l}{\star}}}
	}{}
	\funrule{
		applyCast(\cOOcast{P_1}{l}{P_2},v)
	}{
		\rOOsucc{\vOOcast{v}{\cOOcast{P_1}{l}{P_2}}}
	}{\sidecond{P_1 \smile P_2}}
	\funrule{
		applyCast(\cOOcast{P_1}{l}{P_2},v)
	}{
		\rOOfail{l}
	}{\sidecond{\neg P_1 \smile P_2}}

@@

\begin{definition}[Cast Representation]
	\label{def:cast-rep}
	A cast representation is a set indexed by two types and has four interface 
	functions:
	\begin{description}
		\item[$ id(T) $] constructs an identity cast
		\item[$ seq(c_1,c_2) $] composes two casts
		\item[$ cast(T_1,l,T_2) $] constructs a cast from $ T_1 $ to $ T_2 $
		\item[$ applyCast(c,v) $] applies a cast onto a value
	\end{description}
\end{definition}

To use the framework, users needs to prove that their cast representation is 
\emph{surely LazyD} (Definition~\ref{def:surely-lazyd}).
The definition confines the behavior of $ applyCast(c,v) $ so narrowly that it 
allows the framework to apply casts without referring to the actual definition 
of $ applyCast(c,v) $. This 
is because every casts at runtime is constructed by one of 
the three cast constructors. 
Property (1) handles casts constructed by $ id(T) $. 
And property (2) handles $ seq(c,c) $, which says applying the 
composition of $ c_1 $ and $ c_2 $ is the same as applying $ c_1 $ then $ c_2 $.
All remaining properties handles $ cast(T,l,T) $. They are effectively a 
duplication of the $ applyCast(c,v) $ in \ineffCEKD\ 
(Fig.~\ref{fig:applyCast-D-C}).

\begin{definition}[Surely \lazyD\ Cast Representation]
	\label{def:surely-lazyd}
	A cast representation is surely \lazyD\ if
	\begin{enumerate}
		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
		\item If $ \judgeType{v}{T_1} $,
		$ \judgeTypeFT{c_1}{T_1}{T_2} $, and
		$ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
		then $ applyCast(seq(c_1,c_2),v) = 
		applyCast(c_1,v) >>= \lambda v.applyCast(c_2,v) $ \\
		where 
		\[
		\begin{array}{rcl}
		\rOOsucc{v} >>= f & = & f(v) \\
		\rOOfail{l} >>= f & = & \rOOfail{l}
		\end{array}
		\]
		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
		\item If $ v : \star $, 
		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
		\item If $ v : P_1 $,
		then $ applyCast(cast(\star,l,P_2),\hcvOOinj{P_1}{v}) 
		= applyCast(cast(P_1,l,P_2),v) $
		\item If $ v : P $,
		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
		\item If $ v : \POOunit $,
		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
		\item
		$ 
		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
		= 
		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$

		\item $ applyCast(cast(\POOprod{T_1}{T_2},l,T_3 \times 
		T_4),\hcvOOcons{v_1}{c_1}{v_2}{c_2}) $ \\
		$ = 
		\rOOsucc{(\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))})}
		$ 
		\item $ 
		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinl{v}{c})
		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))})} $
		\item $ 
		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinr{v}{c})
		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_2,l,T_4))})} $
	\end{enumerate}
\end{definition}

@@

	Reduction \fbox{$ \judgeSreduce{C}{s}{s} $}
	\[
	\begin{array}{rclr}
	& \vdots \\
	\redruleS{
		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redruleS{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
	}{}
	\redruleS{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
	}
	\redruleS{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOhalt{(\oOOblame{l})}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
	}
	\end{array}
	\]

@@

In this section we prove \lazyD\ hypercoercion, as a cast representation, is 
correct. First we define $ applyCast(c,v) $ to make it a cast representation, 
then prove that it is surely lazyD, and finally apply 
Theorem~\ref{thm:surely-lazyD-correct} to finish the proof.

%To use hypercoercion as a 
%cast representation in our framework, we need to defined four functions: $ 
%cast(T,l,T) $, $ id(T) $, $ seq(c,c) $, and . We have defined 
%the first three functions in Section~\ref{sec:hypercoercion-definition}. Now 
%we 
%define the $ applyCast(c,v) $  in

\figref{hc-applyCast} defines $ applyCast(c,v) $ for \lazyD\ hypercoercion. 
Applying the identity cast for the 
dynamic type succeeds immediately. When applying a compound cast, we firstly 
apply the middle, then apply the tail. We denote by $ r \; >>= \; f $ to mean 
that if $ r $ is $ \rOOsucc{v} $, the result is $ f(v) $, otherwise the result 
is the failure.
$ applyMiddle(\ell,m,v) $ and $ applyTail(t,v) $ are straightforward.
In the definition of $ applyMiddle(\ell,m,v) $, we generalize 
shallow-consistency to compare middles and values ($ m \smile v $) in the 
natural way.

\begin{figure}
	\fbox{$ applyCast(c,v) = r $}
	\[
	\begin{array}{rclr}
	\funrule{applyCast(\hyperCoercionI,\;v)}{\rOOsucc{v}}{}
	\funrule{applyCast(\hyperCoercionC{?^l}{m}{t},\;\hcvOOinj{P}{v})}{
		applyMiddle(l,m,v) \; >>= \; \lambda v. applyTail(t,v)
	}{}
	\funrule{applyCast(\hyperCoercionC{\epsilon}{m}{t},\;v)}{
		applyMiddle(\epsilon,m,v) \; >>= \; \lambda v. applyTail(t,v)
	}{}
	\end{array}
	\]

	\fbox{$ applyMiddle(\ell,m,v) = v $}
	\[
	\begin{array}{rclr}
	\funrule{applyMiddle(\ell,\POOunit,\hcvOOtt)}{\hcvOOtt}{}
	\funrule{applyMiddle(\ell,\POOfun{c_3}{c_4},\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{
		\hcvOOfun{(c_3 \fatsemi^\ell c_1)}{\rho}{x}{e}{(c_2 \fatsemi^\ell c_4)}
	}{}
	\funrule{applyMiddle(\ell,\POOprod{c_3}{c_4},\hcvOOcons{v_1}{c_1}{v_2}{c_2})}{
		\hcvOOcons{v_1}{(c_1 \fatsemi^\ell c_3)}{v_2}{(c_2 \fatsemi^\ell c_4)}
	}{}
	\funrule{applyMiddle(\ell,\POOsum{c_3}{c_4},\hcvOOinl{v}{c_1})}{
		\hcvOOinl{v}{(c_1 \fatsemi^\ell c_3)}
	}{}
	\funrule{applyMiddle(\ell,\POOsum{c_3}{c_4},\hcvOOinr{v}{c_2})}{
		\hcvOOinr{v}{(c_2 \fatsemi^\ell c_4)}
	}{}
	\funrule{applyMiddle(\ell,m,v)}{
		\rOOfail{l}
	}{
		\sidecond{\ell = l \; \text{and} \; \neg m \smile v}
	}
	\end{array}
	\]

	\fbox{$ applyTail(t,v) = r $}
	\[
	\begin{array}{rclr}
	\funrule{applyTail(\bot^l,v)}{\rOOfail{l}}{}
	\funrule{applyTail(\epsilon,v)}{\rOOsucc{v}}{}
	\funrule{applyTail(!,v)}{\rOOsucc{(\hcvOOinj{P}{v})}}{v : P}
	\end{array}
	\]
	\caption{\lazyD\ hypercoercion's $ applyCast $}
	\label{hc-applyCast}
\end{figure}

>>>>

\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}

@@

\newcommand{\cOOcast}[3]{#1 \overset{#2}{\Rightarrow} #3}

@@

\newcommand{\vOOcast}[2]{#1\langle#2\rangle}

@@

	\redrule{
		\sOOreturn{v}{(
			\mathtt{cast} \; c \; \kappa
			)}
	}{
\begin{cases}
	\sOOreturn{u}{\kappa} & \sidecond{applyCast(v,c) = \rOOsucc{u}}
	\\
	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = \rOOfail{l}}
\end{cases}
	}{}
\redrule{
\sOOreturn{v}{\kOOmt}}{
\sOOhalt{observe(v)}}{}

@@

\todo[inline]{Change the order of parameters for applyCast to take
	the value first and the cast second. -JS
	\\---\\
	Could you tell me why taking the value first is better?
	I am always taking the target of induction first. -KC
	\\---\\
    It's better because it matches the postfix syntax we are using for
    casts. Currently line 2 of applyCast for D is difficult to read,
    compare it with line 4 of applyCast for UD. -JS
    \\---\\
    Does it mean changing the syntax for casts to a prefix syntax would work as 
    well? 
    If yes, I prefer this way, because of the reason in my first response 
    and that function applications (apply) also takes arguments in this order.
    I have fixed it with my idea so that we can see if it works. This change is 
    easy to undo.
    -KC
    \\---\\
    Postfix is better than prefix because then the casts read left to right,
    which is the normal direction for English readers.
    Please make it so. BTW, the way you keep choosing notation etc.
    different from what I'm use to is making it more difficult than
    necessary for me to collaborate with you. If this keeps up,
    I may decide to stop. It's fine for you to ask why, it's not fine
    for you to choose to make things difficult for me. -JS
    \\---\\
    Sorry, I don't indent to make things difficult for you. I have turned to 
    postfix notation. -KC
    }

@@

	\fbox{$applyCast(v,c) = r$}
	\[
	\begin{array}{rclr}
	\funrule{
		applyCast(v,\cOOcast{\star}{l}{\star})
	}{
		\rOOsucc{v}
	}{}
	\funrule{
		applyCast(\vOOcast{v}{\cOOcast{P_1}{l_1}{\star}},\cOOcast{\star}{l_2}{P_2})
	}{
		applyCast(v,\cOOcast{P_1}{l_2}{P_2})
	}{}
	\funrule{
		applyCast(v,\cOOcast{P}{l}{\star})
	}{
		\rOOsucc{\vOOcast{v}{\cOOcast{P}{l}{\star}}}
	}{}
	\funrule{
		applyCast(v,\cOOcast{P_1}{l}{P_2})
	}{
		\rOOsucc{\vOOcast{v}{\cOOcast{P_1}{l}{P_2}}}
	}{\sidecond{P_1 \smile P_2}}
	\funrule{
		applyCast(v,\cOOcast{P_1}{l}{P_2})
	}{
		\rOOfail{l}
	}{\sidecond{\neg P_1 \smile P_2}}

@@

\begin{definition}[Cast Representation]
	\label{def:cast-rep}
	A cast representation is a set indexed by two types and has four interface 
	functions:
	\begin{description}
		\item[$ id(T) $] constructs an identity cast
		\item[$ seq(c_1,c_2) $] composes two casts
		\item[$ cast(T_1,l,T_2) $] constructs a cast from $ T_1 $ to $ T_2 $
		\item[$ applyCast(v,c) $] applies a cast onto a value
	\end{description}
\end{definition}

To use the framework, users needs to prove that their cast representation is 
\emph{surely LazyD} (Definition~\ref{def:surely-lazyd}).
The definition confines the behavior of $ applyCast(v,c) $ so narrowly that it 
allows the framework to apply casts without referring to the actual definition 
of $ applyCast(v,c) $. This 
is because every casts at runtime is constructed by one of 
the three cast constructors. 
Property (1) handles casts constructed by $ id(T) $. 
And property (2) handles $ seq(c,c) $, which says applying the 
composition of $ c_1 $ and $ c_2 $ is the same as applying $ c_1 $ then $ c_2 $.
All remaining properties handles $ cast(T,l,T) $. They are effectively a 
duplication of the $ applyCast(v,c) $ in \ineffCEKD\ 
(Fig.~\ref{fig:applyCast-D-C}).

\begin{definition}[Surely \lazyD\ Cast Representation]
	\label{def:surely-lazyd}
	A cast representation is surely \lazyD\ if
	\begin{enumerate}
		\item If $ v : T $, then $ applyCast(v,id(T)) = \mathtt{succ} \; v $
		\item If $ \judgeType{v}{T_1} $,
		$ \judgeTypeFT{c_1}{T_1}{T_2} $, and
		$ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
		then $ applyCast(v,seq(c_1,c_2)) = 
		applyCast(v,c_1) >>= \lambda v.applyCast(v,c_2) $ \\
		where 
		\[
		\begin{array}{rcl}
		\rOOsucc{v} >>= f & = & f(v) \\
		\rOOfail{l} >>= f & = & \rOOfail{l}
		\end{array}
		\]
		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
		then $ applyCast(v,cast(T_1, l, T_2)) = \rOOfail{l} $
		\item If $ v : \star $, 
		then $ applyCast(v,cast(\TOOdyn,l,\TOOdyn)) = \rOOsucc{v} $
		\item If $ v : P_1 $,
		then $ applyCast(\hcvOOinj{P_1}{v},cast(\star,l,P_2)) 
		= applyCast(v,cast(P_1,l,P_2)) $
		\item If $ v : P $,
		then $ applyCast(v,cast(P,l,\star)) = \rOOsucc{(\hcvOOinj{P}{v})} $
		\item If $ v : \POOunit $,
		then $ applyCast(v,cast(\POOunit,l,\POOunit)) = \rOOsucc{v} $
		\item
		$ 
		applyCast(\hcvOOfun{c_1}{\rho}{x}{b}{c_2}, 
		cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4})) \\
		= 
		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$

		\item $ 
		applyCast(\hcvOOcons{v_1}{c_1}{v_2}{c_2},cast(\POOprod{T_1}{T_2},l,T_3 
		\times 
		T_4)) $ \\
		$ = 
		\rOOsucc{(\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))})}
		$ 
		\item $ 
		applyCast(\hcvOOinl{v}{c},cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}))
		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))})} $
		\item $ 
		applyCast(\hcvOOinr{v}{c},cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}))
		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_2,l,T_4))})} $
	\end{enumerate}
\end{definition}

@@

	Reduction \fbox{$ \judgeSreduce{C}{s}{s} $}
	\[
	\begin{array}{rclr}
	& \vdots \\
	\redruleS{
		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redruleS{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
	}{}
	\redruleS{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\begin{cases}
		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOsucc{v'}} 
		\\
		\sOOhalt{(\oOOblame{l})} \\
		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOfail{l}}
		\end{cases}

	}{}
	\end{array}
	\]

@@

In this section we prove \lazyD\ hypercoercion, as a cast representation, is 
correct. First we define $ applyCast(v,c) $ to make it a cast representation, 
then prove that it is surely lazyD, and finally apply 
Theorem~\ref{thm:surely-lazyD-correct} to finish the proof.

%To use hypercoercion as a 
%cast representation in our framework, we need to defined four functions: $ 
%cast(T,l,T) $, $ id(T) $, $ seq(c,c) $, and . We have defined 
%the first three functions in Section~\ref{sec:hypercoercion-definition}. Now 
%we 
%define the $ applyCast(v,c) $  in

\figref{hc-applyCast} defines $ applyCast(v,c) $ for \lazyD\ hypercoercion. 
Applying the identity cast for the 
dynamic type succeeds immediately. When applying a compound cast, we firstly 
apply the middle, then apply the tail. We denote by $ r \; >>= \; f $ to mean 
that if $ r $ is $ \rOOsucc{v} $, the result is $ f(v) $, otherwise the result 
is the failure.
$ applyMiddle(v,\ell,m) $ and $ applyTail(v,t) $ are straightforward.
In the definition of $ applyMiddle(v,\ell,m) $, we generalize 
shallow-consistency to compare middles and values ($ v \smile m $) in the 
natural way.

\begin{figure}
	\fbox{$ applyCast(v,c) = r $}
	\[
	\begin{array}{rclr}
	\funrule{applyCast(v,\hyperCoercionI,)}{\rOOsucc{v}}{}
	\funrule{applyCast(\hcvOOinj{P}{v},\hyperCoercionC{?^l}{m}{t})}{
		applyMiddle(v,l,m) \; >>= \; \lambda v. applyTail(t,v)
	}{}
	\funrule{applyCast(v,\hyperCoercionC{\epsilon}{m}{t})}{
		applyMiddle(v,\epsilon,m) \; >>= \; \lambda v. applyTail(t,v)
	}{}
	\end{array}
	\]

	\fbox{$ applyMiddle(v,\ell,m) = r $}
	\[
	\begin{array}{rclr}
	\funrule{applyMiddle(\hcvOOtt,\ell,\POOunit)}{\rOOsucc{\hcvOOtt}}{}
	\funrule{applyMiddle(\hcvOOfun{c_1}{\rho}{x}{e}{c_2}\ell,\POOfun{c_3}{c_4})}{
		\rOOsucc{(\hcvOOfun{(c_3 \fatsemi^\ell c_1)}{\rho}{x}{e}{(c_2 
		\fatsemi^\ell c_4)})}
	}{}
	\funrule{applyMiddle(\hcvOOcons{v_1}{c_1}{v_2}{c_2},\ell,\POOprod{c_3}{c_4})}{
		\rOOsucc{(\hcvOOcons{v_1}{(c_1 \fatsemi^\ell c_3)}{v_2}{(c_2 
		\fatsemi^\ell c_4)})}
	}{}
	\funrule{applyMiddle(\hcvOOinl{v}{c_1},\ell,\POOsum{c_3}{c_4})}{
		\rOOsucc{(\hcvOOinl{v}{(c_1 \fatsemi^\ell c_3)})}
	}{}
	\funrule{applyMiddle(\hcvOOinr{v}{c_2},\ell,\POOsum{c_3}{c_4})}{
		\rOOsucc{(\hcvOOinr{v}{(c_2 \fatsemi^\ell c_4)})}
	}{}
	\funrule{applyMiddle(v,l,m)}{
		\rOOfail{l}
	}{
		\sidecond{\neg v \smile m}
	}
	\end{array}
	\]

	\fbox{$ applyTail(v,t) = r $}
	\[
	\begin{array}{rclr}
	\funrule{applyTail(v,\bot^l)}{\rOOfail{l}}{}
	\funrule{applyTail(v,\epsilon)}{\rOOsucc{v}}{}
	\funrule{applyTail(v,!)}{\rOOsucc{(\hcvOOinj{P}{v})}}{}
	\end{array}
	\]
	\caption{\lazyD\ hypercoercion's $ applyCast $}
	\label{hc-applyCast}
\end{figure}
